A Sorting Algorithm Based on Transformer Models

### 2024-06-28 paper/paper.tex
add RevNet and paper

\documentclass{article}
\usepackage{xeCJK}
\setCJKmainfont{SimSong}
\usepackage{graphicx} % Add this line to import the graphicx package

\author{Weizhao Wang}
\date{\today}

@@

\title{A Sorting Algorithm Based on Transformer Models}

\maketitle

@@

@@

\subsection{RevNet}
The RevNet is a novel neural network architecture that is used to model the sorting order of elements in the array. The RevNet consists of multiple layers of reversible residual blocks, each of which is composed of two sub-layers\cite{theefficienttransformer}: a reversible layer and a residual layer. The reversible layer computes the forward and backward transformations of the input sequence, while the residual layer adds the input sequence to the output of the reversible layer. This allows the model to learn the sorting order of elements in the array while preserving the original input sequence.
Here is a simple representation of the RevNet:
\begin{equation}
    x_1,x_2 = chunk(x)
\end{equation}
\begin{equation}
    y_1 = x_1 + F(x_2)
\end{equation}
\begin{equation}
    y_2 = x_2 + G(y_1)
\end{equation}
\begin{equation}
    RevNet(x) = cat(y_1, y_2)
\end{equation}
where $F$ and $G$ are the reversible and residual layers, respectively, and $chunk$ and $cat$ are the chunk and concatenate operations, respectively.

>>>>

\documentclass{article}
\usepackage{xeCJK}
\setCJKmainfont{SimSong}
\usepackage{graphicx}
\usepackage{tikz}

% \author{Weizhao Wang}
% \date{\today}

@@

\begin{tikzpicture}
    [remember picture, overlay]
    \node[anchor=north,yshift=-10mm] at (current page.north) {\includegraphics[width=1.4\textwidth]{picture/head.png}};
\end{tikzpicture}

\vspace{45mm}

@@

\subsubsection*{Multihead}
In this paper, I use 8 heads to build the multihead Attention network, this can enhance the performance of the model wihtout decreasing its accuracy.

@@

\subsection{RevNet}
The RevNet is a novel neural network architecture that is used to model the sorting order of elements in the array. The RevNet consists of multiple layers of reversible residual blocks, each of which is composed of two sub-layers\cite{theefficienttransformer}: a reversible layer and a residual layer. The reversible layer computes the forward and backward transformations of the input sequence, while the residual layer adds the input sequence to the output of the reversible layer. This allows the model to learn the sorting order of elements in the array while preserving the original input sequence.
Here is a simple representation of the RevNet:
\begin{equation}
    x_1,x_2 = chunk(x)
\end{equation}
\begin{equation}
    y_1 = x_1 + F(x_2)
\end{equation}
\begin{equation}
    y_2 = x_2 + G(y_1)
\end{equation}
\begin{equation}
    RevNet(x) = cat(y_1, y_2)
\end{equation}
where $F$ and $G$ are the reversible and residual layers,such as Attention, respectively, and $chunk$ and $cat$ are the chunk and concatenate operations, respectively.
and its inverse format is
\begin{equation}
    y_1,y_2 = chunk(y)
\end{equation}
\begin{equation}
    x_2 = y_2 - G(y_1)
\end{equation}
\begin{equation}
    x_1 = y_1 - F(x_2)
\end{equation}
\begin{equation}
    InvRevNet(y) = cat(x_1,x_2)
\end{equation}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]
    {picture/RevNet.png}

    {left: forward  right: inverse}
    \caption{RevNet Structure}
    \label{RevNet Structure}
\end{figure}
